---
title: "FLewis_Week2_HW"
author: "Fayliette Lewis"
date: "7/30/2021"
output: html_document
---

#
**1. Use the summary function to gain an overview of the data set. Then display the mean and median for at least two attributes.**

```{r}

library(readr)
library("dplyr") 

# data set GitHub url
ghub_url <- "https://raw.githubusercontent.com/Fayliette/MSDS_R/main/DoctorVisits.csv"

# Load data set and exclude first column which shows row count
dv_df <- read.csv(ghub_url, stringsAsFactors = FALSE)[2:13]

# Display the first 6 rows of the data set
head(dv_df)

# Get the  overview of the data set
summary(dv_df)

# Display the mean and median of the age and income attributes
summarize(dv_df, mean_income = mean(income, na.rm=TRUE), median_income = median(income, na.rm=TRUE),
          mean_age = mean(age, na.rm=TRUE), median_age = median(age, na.rm=TRUE))

```

#
**2. Create a new data frame with a subset of the columns and rows. Make sure to rename it.**

```{r}
female_dv <- subset(dv_df[1:5], gender=="female" & illness > 2)

# Display the first 6 rows of the new data frame
head(female_dv)

```
#
**3. Create new column names for the new data frame.**

```{r}

colnames(female_dv) <- c("F_visits", "sex", "F_age", "F_income", "F_illness" )
head(female_dv)

```
#
**4. Use the summary function to create an overview of your new data frame. Then print the mean and median for the same two attributes. Please compare**

```{r}

summary(female_dv)
summarize(female_dv, F_mean_income = mean(F_income, na.rm=TRUE), F_median_income = median(F_income, na.rm=TRUE),
          F_mean_age = mean(F_age, na.rm=TRUE), F_median_age = median(F_age, na.rm=TRUE))

```

#
**5. For at least 3 values in a column please rename so that every value in that column is renamed. For example, suppose I have 20 values of the letter “e” in one column. Rename those values so that all 20 would show as “excellent”.**

```{r}

new_dv_df <- mutate(dv_df, gender = ifelse(gender == "female", "F", "M"), 
                    private = ifelse(private == "yes", "Y", "N"),
                    illness = ifelse(illness > 3, "moderate - high illness", "no - mild illness"))
head(new_dv_df)
```

